%%%% Proceedings format for most of ACM conferences (with the exceptions listed below) and all ICPS volumes.
\documentclass[sigconf]{acmart}
%%%% As of March 2017, [siggraph] is no longer used. Please use sigconf (above) for SIGGRAPH conferences.

%%%% Proceedings format for SIGPLAN conferences 
% \documentclass[sigplan, anonymous, review]{acmart}

%%%% Proceedings format for SIGCHI conferences
% \documentclass[sigchi, review]{acmart}

%%%% To use the SIGCHI extended abstract template, please visit
% https://www.overleaf.com/read/zzzfqvkmrfzn


\usepackage{booktabs} % For formal tables
\usepackage{amsmath} % For better math equations
\usepackage{amsthm} % For better theorem structures
\usepackage[ruled]{algorithm2e} % For algorithms
\usepackage{subcaption} % For multiple images in a section

\renewcommand{\algorithmcfname}{ALGORITHM}

% Theorem section style and definition
\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[section]

% Definition section style and definition
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]

% Copyright
% \setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}


% DOI
% \acmDOI{10.475/123_4}

% ISBN
% \acmISBN{123-4567-24-567/08/06}

%Conference
\acmConference[CS 597 Spring'19 UIC]{UIC}{April 2019}{Chicago, Illinois USA}
\acmYear{2019}
\copyrightyear{2019}


\acmArticle{4}
\acmPrice{15.00}



\begin{document}
\title{Fairness of Envy-freeness in Maximum Nash Welfare of Specialized Markets}


\author{Shail Rakhunde}
\affiliation{%
  \institution{University of Illinois at Chicago}
  \city{Chicago}
  \state{Illinois}
}
\email{srakhu2@uic.edu}


\begin{abstract}
Influence and information flow is inherent and inseparable part of most of the graphs. Graphs showcase patterns not only in the structure but also in the flow of the information through the structure. Specifically, some of the networks like social media, needs a different treatment than other networks as each node and the edge represent a person and their inherent, impulse action in a day to day life. Defining the network this way makes us understand that the flow of information is equally or sometimes more important than the structure of the network itself.

Conventional influence learning approaches focus on building hand-crafted rules to perform feature engineering on each type of transactions between various nodes. This necessitates a deep knowledge of network domain. Also, it is often difficult to manually analyze and engineer the latent, high-dimensional, obscure features which are observed to provide a better representation of the network. Node embedding has recently emerged as an effective and scalable tool for mining all kinds of a networks. Deep learning based node embedding methods are able to identify and learn complex latent features in much simpler ways. Inspired by their results, in this paper we'll try to understand how to extend node embeddings for networks with directional information flow. We propose InfloWalk, a method to learn network embeddings based on network structure and the flow of information/influence in the network. On higher level, InfloWalk performs intelligent walks over the network following the flow of influence. Further, we will perform some experiments on real world datasets to analyze the effectiveness of the proposed method.


\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below.
%
 \begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10002951.10003227.10003351</concept_id>
<concept_desc>Information systems~Data mining</concept_desc>
<concept_significance>500</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Information systems~Data mining}

\keywords{Network Embedding, Influence Embedding, Representation Learning, Social Networks}

\maketitle

\input{samplebody-conf}

\bibliographystyle{ACM-Reference-Format}
\bibliography{sample-bibliography}

\end{document}
